Stage-Splitting a Modal Language

### 2014-10-31 paper/splitting.tex
small changes; lots of commenting-out

Splitting a function is more complex, because function bodies are open terms,
and so are split by the judgments described in the next subsection. Essentially,
functions will split into two functions, whose bodies correspond to the stage
\bbone\ and stage \bbtwo\ components of the original function body.

\TODO talk about the changed function signature, which is necessitated by the precomputation;
note that we have to assume {\em all} stage \bbone\ functions have meaningful precomputations

@@

\subsection {Notable Properties}

\nr{These points will probably get lifted into the preceding sections.}

There are some particularly notable features of this definition of term
splitting.

\paragraph {Stage \bbone\ Divergence}

In the splitting rules for stage \bbone\ {\tt if} and {\tt case} expressions, we
have enough information at stage \bbone\ to know what branch to take, so there's
no need to speculate. Instead, we evaluate the stage \bbone\ portion of the
taken branch only, and inject the precomputation into a sum type. In the
resumer, we case on that injection, and resume the stage \bbtwo\ portion of the
correct branch.

\paragraph {Stage \bbone\ Functions}

The body of a stage \bbone\ function may contain stage \bbtwo\ computation. We
handle this by splitting the function into two functions: one in the immediate
result which handles all the stage \bbone\ content of the original, and one in
the resumer which handles all of the stage \bbtwo\ content. Note that stage
\bbone\ lambdas are partial values, and so have only a trivial precomputation.

\paragraph {Typing the Boundary}

\TODO add the example which shows that we need dynamic types

@@

\subsection{Cost}

>>>>

Splitting a function is more complex, because function bodies are open terms,
and so are split by the judgments described in the next subsection. Essentially,
functions will split into two functions, whose bodies correspond to the stage
\bbone\ and stage \bbtwo\ components of the original function body.
Moreover, the body of the function may contain a precomputation,
which should be saved and resumer appropriately wherever the function is applied.

@@

In the splitting rules for stage \bbone\ {\tt case} expressions, we
have enough information at stage \bbone\ to know what branch to take, so there's
no need to speculate. Instead, we evaluate the stage \bbone\ portion of the
taken branch only, and inject the precomputation into a sum type. In the
resumer, we case on that injection, and resume the stage \bbtwo\ portion of the
correct branch.

%\subsection {Notable Properties}
%
%\nr{These points will probably get lifted into the preceding sections.}
%
%There are some particularly notable features of this definition of term
%splitting.

%\paragraph {Stage \bbone\ Divergence}
%

%\paragraph {Stage \bbone\ Functions}
%
%The body of a stage \bbone\ function may contain stage \bbtwo\ computation. We
%handle this by splitting the function into two functions: one in the immediate
%result which handles all the stage \bbone\ content of the original, and one in
%the resumer which handles all of the stage \bbtwo\ content. Note that stage
%\bbone\ lambdas are partial values, and so have only a trivial precomputation.
%
%\paragraph {Typing the Boundary}
%
%\TODO add the example which shows that we need dynamic types

@@

\subsection{Eliminating Unnecessary Code}
